Collaboration in Ad Hoc Teamwork: \\ Ambiguous Tasks, Roles, and Communication\vspace{1em}

### 2015-11-30 paper/adhoccom.tex
added acknowledgement LARG group

Work partially supported by INRIA, Conseil R\'{e}gional d'Aquitaine, the ERC grant EXPLORERS 24007, and a INRIA Explorer fellowship.

>>>>

Work partially supported by INRIA, Conseil R\'{e}gional d'Aquitaine, the ERC grant EXPLORERS 24007, and a INRIA Explorer fellowship. A portion of this work has taken place in the Learning Agents Research Group (LARG) at the Artificial Intelligence Laboratory, The University of Texas at Austin.  LARG research is supported in part by grants from the National Science Foundation (CNS-1330072, CNS-1305287), ONR (21C184-01), AFRL (FA8750-14-1-0070), AFOSR (FA9550-14-1-0087), and Yujin Robot.
